Naturalness in U(1) exentions of the MSSM

### 2014-11-09 paper/e6ssm-tuning-paper.tex
added more references.

U(1) literature review  \newline

@@

\section{\label{sec:model}The Model}

>>>>

U(1) literature review  \newline
 Here we will refer to U(1) extensions of the MSSM, which solve the $\mu$-problem as the USSM \cite{Fayet:1977yc,Suematsu:1994qm,Cvetic:1995rj}, while will sometimes specify that the models are inspired by $E_6$ by referring to them as such. Finally we will aslo discuss specific models with complete $E_6$ matter multiplets at low energies and an extra $U(1)$ under which the right handed neutrino remains interactionless as E$_6$SSM-variants, with the E$_6$SSM reserved for the original formualtion of this model \cite{King:2005jy,King:2005my,Athron:2010zz} original formulation of the model.

$U(1)$ and $E_6$ inspired extensions of the MSSM have been studied very widely in the literature \cite{Gunion:1989we,Gunion:1992hs,Binetruy:1985xm,Ellis:1986yg,Ibanez:1986si,Gunion:1986ky,Haber:1986gz,Baer:1987eb,Gunion:1987jd,Grifols:1986vr,Morris:1987fm,Suematsu:1997tv,Suematsu:1997qt,Suematsu:1997au,Keith:1996fv,Gherghetta:1996yr} (or for reviews see \cite{Hewett:1988xc,Langacker:2008yv}).   More recently...

@@

The structure of this paper is as follows.  In section \ref{sec:model} we review the models we consider.  In section \ref{sec:ewsb} we speciofy the EWSB conditions of the moidels, with particular focus on how the $Z^\prime$ mass influences the predition of $M_Z$.  Then in section \ref{sec:tuning} we introduce our fine tuning measure and our approach to evaluating it to obtain the individual sensitivities.  The numerical procedure we use to obtain our results is given in \ref{subsec:numericalprocedure} and then the reulst are specified in section \ref{sec:results}.

\section{\label{sec:model}U(1) extensiosn and the E$_6$SSM}
